Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-30 manuscript/manuscript.Rmd
added abstract in

abstract: |
  Write something here

@@

Eq. \eqref{eq:may} is an interesting study case of a *tipping point* (saddle-node bifurcation) (see Fig. \ref{fig:may stable}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $\hat X_t$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.
This also creates the phenomenon of *hysteresis*, where returning $H$ to its original value is not sufficient to restore $\hat X_t$ to the original stable state.

\begin{figure}
  \centering
  \includegraphics[width = 0.8\linewidth]{figures/MayStablePoints.pdf}
  \caption{
    \label{fig:may stable}
    The fixed point diagram for the model [@may77] associated to $f_{\text{May}}$ as a function of varying the parameter $\beta H$.
    That is, these are the zeroes of the function $f_{\text{May}}$. 
    Stable fixed points (also known as *attractors*) are plotted using a solid line, while the unstable fixed point is shown as a dotted line.
  }
\end{figure}

>>>>

abstract: |
  TBD Change slightly!!!!!
  Existing methods for optimal control methods struggle to deal with the
  complexity commonly encountered in real-world systems, including
  dimensionality, process error, model bias and heterogeneity.  Instead
  of tackling these complexities directly, researchers have typically
  sought to find exact optimal solutions to simplified models of the
  processes in question. When is the optimal solution to a very
  approximate, stylized model better than an approximate solution to a
  more accurate model? This question has largely gone unanswered owing
  to the difficulty of finding even approximate solutions in the case of
  complex models.  Our approach draws on recent algorithmic and
  computational advances in deep reinforcement learning. These methods
  have hitherto focused on problems in games or robotic mechanics, which
  operate under precisely known rules. We demonstrate the ability for
  novel algorithms using deep neural networks to successfully
  approximate such solutions (the ‘‘policy function’’ or control rule)
  without knowing or ever attempting to infer a model for the process
  itself. This powerful new technique lets us finally begin to answer
  the question. We show that in many but not all cases, the optimal
  policy for a carefully chosen over-simplified model can still
  out-perform these novel algorithms trained to find approximate
  solutions to simulations of a realistically complex system. Comparing
  these two approaches can lead to insights in the importance of
  real-world features of observation and process error, model biases,
  and heterogeneity.

@@

Eq. \eqref{eq:may} is an interesting study case of a *tipping point* (saddle-node bifurcation) (see Fig. \ref{fig:may}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $\hat X_t$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.
This also creates the phenomenon of *hysteresis*, where returning $H$ to its original value is not sufficient to restore $\hat X_t$ to the original stable state.

```{r}
#| label: may
#| fig.cap: "The fixed point diagram for the model associated to $f_{\\text{May}}$ as a function of varying the parameter $\\beta H$.
#| That is, these are the zeroes of the function $f_{\\text{May}}$. 
#| Stable fixed points (also known as *attractors*) are plotted using a solid line, while the unstable fixed point is shown as a dotted line."
#| out.width: "6.5in"

knitr::include_graphics("figures/MayStablePoints.pdf")
```
